---
title: "Online assessment methods"
icon: /icons/tools.png
menuicon: /icons/tools-menu.png
date: 2020-07-31T11:05:44+02:00
expandable: false
instructions: false
weight: 3
---


## Digital assessment
Click [here](https://werkgroep-toetsen-op-afstand.github.io/remote-assessment-aid/methods/digital_assessment/) for more information on digital assessment.  
<br>

**Tips for this assessment method**

* If the assessment will also be taken by other students (e.g. at a different time), present the questions in random order to prevent the sharing of answers. 

* Live proctoring is quite feasible in the case of individual assessments.

```{r, child="../../snippets/knowledge/know_methods_limitations.en.md"}
```

## Presentations
Click [here]( https://werkgroep-toetsen-op-afstand.github.io/remote-assessment-aid/methods/presentation) for more information on presentations.  
<br>

**Tips for this assessment method**

```{r, child="../../snippets/knowledge/know_methods_questions.en.md"}
```

```{r, child="../../snippets/knowledge/know_methods_ID.en.md"}
```

## Oral exams
Click [here]( https://werkgroep-toetsen-op-afstand.github.io/remote-assessment-aid/methods/oral_exam/) for more information on oral exams.  
<br>

**Tips for this assessment method**

```{r, child="../../snippets/knowledge/know_methods_questions.en.md"}
```

## Observations
Click [here](https://werkgroep-toetsen-op-afstand.github.io/remote-assessment-aid/methods/observations/) for more information on observations.  
<br> 

**Tips for this assessment method**

```{r, child="../../snippets/knowledge/know_methods_questions.en.md"}
```

## Portfolio
Click [here]( https://werkgroep-toetsen-op-afstand.github.io/remote-assessment-aid/methods/portfolio/) for more information on portfolios.  
<br> 

## Projects and products
Click [here]( https://werkgroep-toetsen-op-afstand.github.io/remote-assessment-aid/methods/project_product/) for more information on projects and products.  
